Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2023-11-10 analysis/paper/paper.qmd
Lombard requested tcsa data, which I only had in dataframe. I created excel files for tcsa values. One with all, one without outliers.

>>>>

# save the tcsa dataframe as xlsx as Lombard requested

# install.packages('writexl')
# library(writexl)
# 
# write_xlsx(tcsa, here::here("analysis/data/derived_data/tcsa_omit_large_tcsa.xlsx"))
# 
# # raw tcsa data including outliers.
# tcsa_all_data <- mydata %>%
#   mutate(min_tcsa = 0.5 *Width * Thickness) %>%
#  # mutate(max_tcsa = 0.5 *Length * Thickness) %>%
#   # dplyr::filter(min_tcsa <= 250) %>% #omit very large TCSA, could be measurement error
#   # group rare raw materials < 10
#   mutate(raw_materials_top = fct_lump_min(Raw_material, 10)) %>%
#   mutate(site_name_top = fct_lump_min(Site_name, 5))
# 
# write_xlsx(tcsa_all_data, here::here("analysis/data/derived_data/tcsa_all.xlsx"))
